Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-26 manuscript/manuscript.Rmd
Update manuscript.Rmd

Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modelling tasks. Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a]. In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data. In the following sections of this paper, we then consider whether adding attention to an model that uses embeddings can provide better predictive accuracy. The following is intended as a high level review of some of the relevant theory behind attention based approaches; for more technical details the sources quoted in this section can be consulted.

>>>>

Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modelling tasks. Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural langauge processing are demonstrated in, for example, [@Vaswani2017a]. In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the modelling task. In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data. In the following sections of this paper, we then consider whether adding attention to an model that uses embeddings can provide better predictive accuracy. The following is intended as a high level review of some of the relevant theory behind attention based approaches; for more technical details the sources quoted in this section can be consulted.
